---
title: "Interpolation of biodiversity change in global mammals at Holocene time scale"
author: "Petr Keil"
date: "Sept 17, 2021"
output: 
  html_document: 
    highlight: pygments
    number_sections: yes
    theme: cerulean
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
  knitr::opts_chunk$set(echo = TRUE)
```

## Load and import data and other objects

```{r, message=FALSE, warning=FALSE}
rm(list = ls())
set.seed(1234)

source("functions_settings_libraries.r")
load(file = "mammals_20kg_processed.RData")

# limits for plots showing observed vs predicted values of change
lims.delta <- c(-60, 15)

objects()
```

## Log Ratios (LR) of species richness change

```{r}
CNTR@data <- data.frame(CNTR@data, 
                        LR = log10(CNTR@data$S.curr / CNTR@data$S.natu))

HEX@data <- data.frame(HEX@data, 
                        LR = log10(HEX@data$S.curr / HEX@data$S.natu))

```

## Plot the raw data

"Fortify" `sp` objects so that they are suitable for ggplot2.

```{r, warning = FALSE}
  CNTR.fort <- fortify(CNTR, region = "LEVEL3_NAM") %>%
               left_join(y = CNTR@data, by = c("id" = "LEVEL3_NAM"))

  HEX.fort <- fortify(HEX, region = "id") %>%
              left_join(y = HEX@data, by = "id")
  
  LAND.fort <- fortify(LAND)
```

Observed *true* species numbers in countries:

```{r, fig.width = 10, fig.height = 7, eval = TRUE}
  pCNTR.S1 <-ggplot(CNTR.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.natu)) + blank.theme +
             geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                          fill = NA, colour = "black") +
             coord_fixed() + labs(subtitle = "Past S") +
             scale_fill_viridis(option = "magma", limits = c()) 
  pCNTR.S2 <-ggplot(CNTR.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.curr)) + blank.theme +
             geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                          fill = NA, colour = "black") +
             coord_fixed() + labs(subtitle = "Current S") +
             scale_fill_viridis(option = "magma") 
  pCNTR.ga <-ggplot(CNTR.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.gain)) + blank.theme +
             geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                          fill = NA, colour = "black") +
             coord_fixed() + labs(subtitle = "Gain") +
             scale_fill_viridis(option = "magma") 
  pCNTR.lo <-ggplot(CNTR.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.loss)) + blank.theme +
                 geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                          fill = NA, colour = "black") +
             coord_fixed() + labs(subtitle = "Loss") +
             scale_fill_viridis(option = "magma") 
  pCNTR.de <-ggplot(CNTR.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.delta)) + blank.theme +
             geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                          fill = NA, colour = "black") +
             coord_fixed() + labs(subtitle = "S change") +
             scale_fill_viridis(option = "magma", limits = lims.delta) 

  grid.arrange(pCNTR.S1, pCNTR.S2, pCNTR.ga, pCNTR.lo, pCNTR.de, ncol = 2, nrow = 3)
```

Countries sampled in time 1 or time 2:

```{r, eval = TRUE}
pCNTR.smp <- ggplot(CNTR.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = time.sampled), colour = "black") + blank.theme +
             coord_fixed() + labs() +
             scale_fill_grey() 
pCNTR.smp
```

Observed *true* species numbers in hexagons:

```{r, fig.width = 10, fig.height = 7, eval=TRUE}
  pHEX.S1 <- ggplot(HEX.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.natu)) + blank.theme +
             geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                          fill = NA, colour = "black") +
             coord_fixed() + labs(subtitle = "Past S") +
             scale_fill_viridis(option = "magma", limits = c()) 
  pHEX.S2 <- ggplot(HEX.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.curr)) + blank.theme +
             geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                                    fill = NA, colour = "black") +
             coord_fixed() + labs(subtitle = "Current S") +
             scale_fill_viridis(option = "magma") 
  pHEX.ga <- ggplot(HEX.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.gain)) + blank.theme +
             geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                          fill = NA, colour = "black") +
             coord_fixed() + labs(subtitle = "Gain") +
             scale_fill_viridis(option = "magma") 
  pHEX.lo <- ggplot(HEX.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.loss)) + blank.theme +
             geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                          fill = NA, colour = "black") +
             coord_fixed() + labs(subtitle = "Loss") +
             scale_fill_viridis(option = "magma") 
  pHEX.de <- ggplot(HEX.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.delta)) + blank.theme +
             geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                          fill = NA, colour = "black") +
             coord_fixed() + labs(subtitle = "S change") +
             scale_fill_viridis(option = "magma", limits = lims.delta) 

  grid.arrange(pHEX.S1, pHEX.S2, pHEX.ga, pHEX.lo, pHEX.de, ncol = 2, nrow = 3)
```


# Interpolation using the SAR method

## Fit boosted trees

```{r}
NTREES <- 1000
SAR.gbm <- gbm(S ~ Lon + Lat + Area.km + time, 
                       data = CNTR.sub, 
                       interaction.depth = 10,
                       distribution = "poisson",
                       n.minobsinnode = 3,
                       n.trees = NTREES)
```

## Predict to countries (SAR method)

```{r}
preds <- data.frame(CNTR.L, 
                    S.pred = predict(SAR.gbm, newdata = CNTR.L,
                                     n.trees = NTREES, type = "response"))

pred.wide <- reshape(data = preds,
                     idvar = "LEVEL3_NAM",
                     v.names = c("S", "S.pred"),
                     timevar = "time",
                     direction = "wide") %>% select(LEVEL3_NAM, 
                                                    S.pred.2, 
                                                    S.pred.1,
                                                    S.1,
                                                    S.2)

pred.wide <- data.frame(pred.wide, 
                        LR.SAR = log10(pred.wide$S.pred.2 / pred.wide$S.pred.1),
                        S.delta.SAR = pred.wide$S.pred.2 - pred.wide$S.pred.1)

CNTR.pred <- CNTR
CNTR.pred@data <- left_join(x = CNTR.pred@data,
                            y = pred.wide,
                            by = "LEVEL3_NAM")

# replace Inf values of log ratios by NAs
CNTR.pred@data$LR[CNTR.pred@data$LR == Inf] <- NA 

# Pearson correlations of observed vs predicted
delta.cor.cntr.sar <- round(cor(CNTR.pred@data$S.delta, 
                                CNTR.pred@data$S.delta.SAR, 
                                use = "complete.obs"), 3)
delta.cor.cntr.sar

LR.cor.cntr.sar <- round(cor(CNTR.pred@data$LR, 
                             CNTR.pred@data$LR.SAR, 
                             use = "complete.obs"), 3)
LR.cor.cntr.sar
```

## Plot predicted vs observed in countries (SAR method)

```{r, fig.width=10, fig.height=5, warning=FALSE, message=FALSE}
SAR.obspred.CNTR.S <- ggplot(data = CNTR.pred@data, aes(x = S.delta, y = S.delta.SAR)) +
  geom_point(colour="#377eb8", shape = 1) + 
  geom_abline(intercept=0, slope=1) + 
  theme(aspect.ratio=1) + coord_fixed() +
  geom_hline(yintercept=0, linetype =2) +
  geom_vline(xintercept=0, linetype =2) +
  xlim(-60,16) + ylim(-60,16) +
  xlab(TeX(r'($\True \; \hat{S}_{\Delta}$)')) + 
  ylab(TeX(r'($\Predicted \; \hat{S}_{\Delta}$)')) +  
  labs(subtitle = paste("Pearson cor. = ", delta.cor.cntr.sar)) +
  theme_bw() 

SAR.obspred.CNTR.LR <- ggplot(data = CNTR.pred@data, aes(x = LR, y = LR.SAR)) +
  geom_point(colour="#377eb8", shape = 1) + 
  geom_abline(intercept=0, slope=1) + 
  theme(aspect.ratio=1) + coord_fixed() +
  geom_hline(yintercept=0, linetype =2) +
  geom_vline(xintercept=0, linetype =2) +
  xlim(-1.2, 2) + ylim(-1.2, 2) +
  xlab("True LR") + ylab("Predicted LR") + 
  labs(subtitle = paste("Pearson cor. = ", LR.cor.cntr.sar)) +
  theme_bw() 

grid.arrange(SAR.obspred.CNTR.S, SAR.obspred.CNTR.LR, nrow=1, ncol=2)
```

## Predict to hexagons (SAR method)

```{r}
HEX.preds <- rbind(HEX@data, HEX@data)
HEX.preds <- data.frame(HEX.preds, time = rep(1:2, each = nrow(HEX@data)))


HEX.preds <- data.frame(HEX.preds, 
                        S.pred = predict(SAR.gbm, 
                                         newdata = HEX.preds,
                                         n.trees = NTREES, 
                                         type = "response"))

HEX.preds.wide <- reshape(data = HEX.preds,
                           idvar = "id",
                           v.names = "S.pred",
                           timevar = "time",
                           direction = "wide") %>% select(id, 
                                                          S.pred.2, 
                                                          S.pred.1)

HEX.preds.wide <- data.frame(HEX.preds.wide, 
                             S.delta.SAR = HEX.preds.wide$S.pred.2 -
                                           HEX.preds.wide$S.pred.1,
                             LR.SAR = log10(HEX.preds.wide$S.pred.2 /
                                            HEX.preds.wide$S.pred.1))


HEX.pred <- HEX
HEX.pred@data <- left_join(x = HEX.pred@data,
                           y = HEX.preds.wide,
                           by = "id")

# replace Inf values of log ratios by NAs
HEX.pred@data$LR[HEX.pred@data$LR == Inf] <- NA 
HEX.pred@data$LR.SAR[HEX.pred@data$LR.SAR == Inf] <- NA 

# Pearson correlations of observed vs predicted
delta.cor.hex.sar <- round(cor(HEX.pred@data$S.delta, 
                               HEX.pred@data$S.delta.SAR, 
                               use = "complete.obs"), 3)
delta.cor.hex.sar

LR.cor.hex.sar <- round(cor(HEX.pred@data$LR, 
                            HEX.pred@data$LR.SAR, 
                            use = "complete.obs"), 3)
LR.cor.hex.sar
```

## Plot predicted vs observed in hexagons (SAR method)

```{r, fig.width = 10, fig.height = 5, warning=FALSE, message=FALSE}
SAR.obspred.HEX.S <- ggplot(data = HEX.pred@data, aes(x = S.delta, y = S.delta.SAR)) +
  geom_point(colour="#377eb8", shape = 1) + 
  geom_abline(intercept=0, slope=1) + 
  theme(aspect.ratio=1) + coord_fixed() +
  geom_hline(yintercept=0, linetype =2) +
  geom_vline(xintercept=0, linetype =2) +
  xlim(-60,16) + ylim(-60,16) +
  xlab(TeX(r'($\True \; \hat{S}_{\Delta}$)')) + 
  ylab(TeX(r'($\Predicted \; \hat{S}_{\Delta}$)')) +  
  labs(subtitle = paste("Pearson cor. = ", delta.cor.hex.sar)) +
  theme_bw() 

SAR.obspred.HEX.LR <- ggplot(data = HEX.pred@data, aes(x = LR, y = LR.SAR)) +
  geom_point(colour="#377eb8", shape = 1) + 
  geom_abline(intercept=0, slope=1) + 
  theme(aspect.ratio=1) + coord_fixed() +
  geom_hline(yintercept=0, linetype =2) +
  geom_vline(xintercept=0, linetype =2) +
  xlab("True LR") + ylab("Predicted LR") + 
  labs(subtitle = paste("Pearson cor. = ", LR.cor.hex.sar)) +
  theme_bw() 

grid.arrange(SAR.obspred.HEX.S, SAR.obspred.HEX.LR, nrow=1, ncol=2)
```

# Interpolation using the OAR method

## Fit boosted trees

Beware: This may take a couple of minutes.

```{r}
NTREES <- 1000

OAR.gbm <- gbm(occ ~ Lon + Lat + Area.km + time + species, 
               data = CNTR.sub.OAR, 
               interaction.depth = 10, 
               distribution = "bernoulli",
               n.minobsinnode = 3,
               n.trees = NTREES)
```

## Predict to countries (OAR method)

```{r}
CNTR.forpred.1 <- CNTR.forpred.OAR[CNTR.forpred.OAR$time == 1, ]
CNTR.forpred.2 <- CNTR.forpred.OAR[CNTR.forpred.OAR$time == 2, ]

P1 <- predict(OAR.gbm, 
              newdata = CNTR.forpred.1, 
              type = "response",
              n.trees = NTREES)
P2 <- predict(OAR.gbm, 
              newdata = CNTR.forpred.2, 
              type = "response",
              n.trees = NTREES)
P.ext = P1 * (1-P2) # probability of extinction
P.gain = P2 * (1-P1) # probability of gain

T.all <- data.frame(P.ext, P.gain, P1, P2, CNTR.forpred.1)

preds <- ddply(.data = T.all, 
                 .variables=c("LEVEL3_NAM"),
                 .fun=summarize,
                 est.S1 = sum(P1),
                 est.S2 = sum(P2),
                 est.Gain = sum(P.gain),
                 est.Loss =  - sum(P.ext),
                 S.delta.OAR = est.Gain + est.Loss,
                 LR.OAR = log10(sum(P2)/sum(P1)))

CNTR.pred2 <- CNTR.pred
CNTR.pred2@data <- left_join(x = CNTR.pred2@data,
                            y = preds,
                            by = "LEVEL3_NAM")

# replace Inf values of log ratios by NAs
CNTR.pred2@data$LR[CNTR.pred2@data$LR == Inf] <- NA 
CNTR.pred2@data$LR.SAR[CNTR.pred2@data$LR.SAR == Inf] <- NA 

# Pearson correlations of observed vs predicted
delta.cor.cntr.oar <- round(cor(CNTR.pred2@data$S.delta, 
                                CNTR.pred2@data$S.delta.OAR, 
                                use = "complete.obs"), 3)
delta.cor.cntr.oar

LR.cor.cntr.oar <- round(cor(CNTR.pred2@data$LR, 
                             CNTR.pred2@data$LR.OAR, 
                             use = "complete.obs"), 3)
LR.cor.cntr.oar
```

## Plot predicted vs observed in countries (OAR method)

```{r, fig.width = 10, fig.height=5, warning=FALSE, message=FALSE}
OAR.obspred.CNTR.S <- ggplot(data = CNTR.pred2@data, 
                      aes(x = S.delta, y = S.delta.OAR)) +
  geom_point(colour = "#377eb8", shape = 1) + 
  geom_point(aes(x = S.gain, y = est.Gain), colour = "#4daf4a", shape = 1) +
  geom_point(aes(x = S.loss, y = est.Loss), colour = "#e41a1c", shape = 1) +
  geom_abline(intercept=0, slope=1) + 
  theme(aspect.ratio=1) + coord_fixed() +
  geom_hline(yintercept=0, linetype =2) +
  geom_vline(xintercept=0, linetype =2) +
  xlim(-60,16) + ylim(-60,16) +
  labs(subtitle = paste("Pearson cor. = ", delta.cor.cntr.oar)) +
  xlab("True") + ylab("Predicted") + theme_bw()

OAR.obspred.CNTR.LR <- ggplot(data = CNTR.pred2@data, 
                      aes(x = LR, y = LR.OAR)) +
  geom_point(colour = "#377eb8", shape = 1) + 
  geom_abline(intercept=0, slope=1) + 
  theme(aspect.ratio=1) + coord_fixed() +
  geom_hline(yintercept=0, linetype =2) +
  geom_vline(xintercept=0, linetype =2) +
  labs(subtitle = paste("Pearson cor. = ", LR.cor.cntr.oar)) +
  xlab("True LR") + ylab("Predicted LR") + theme_bw()

grid.arrange(OAR.obspred.CNTR.S, OAR.obspred.CNTR.LR, nrow=1, ncol=2)
```

## Predict to hexagons (OAR method)

```{r, warning=FALSE, message=FALSE}
HEX.forpred.1 <- HEX.forpred.OAR[HEX.forpred.OAR$time == 1, ]
HEX.forpred.2 <- HEX.forpred.OAR[HEX.forpred.OAR$time == 2, ]

P1 <- predict(OAR.gbm, 
              newdata = HEX.forpred.1, 
              type = "response",
              n.trees = NTREES)
P2 <- predict(OAR.gbm, 
              newdata = HEX.forpred.2, 
              type = "response",
              n.trees = NTREES)
P.ext = P1 * (1-P2) # probability of extinction
P.gain = P2 * (1-P1) # probability of gain

T.all <- data.frame(P.ext, P.gain, P1, P2, HEX.forpred.1)


preds <- ddply(.data = T.all, 
                 .variables=c("id"),
                 .fun=summarize,
                 est.S1 = sum(P1),
                 est.S2 = sum(P2),
                 est.Gain = sum(P.gain),
                 est.Loss =  - sum(P.ext),
                 S.delta.OAR = est.Gain + est.Loss,
                 LR.OAR = log10(sum(P2)/sum(P1)))

HEX.pred2 <- HEX.pred
HEX.pred2@data <- left_join(x = HEX.pred2@data,
                            y = preds,
                            by = "id")

# replace Inf values of log ratios by NAs
HEX.pred2@data$LR[HEX.pred2@data$LR == Inf] <- NA 
HEX.pred2@data$LR.SAR[HEX.pred2@data$LR.SAR == Inf] <- NA 

# Pearson correlations of observed vs predicted
delta.cor.hex.oar <- round(cor(HEX.pred2@data$S.delta, 
                               HEX.pred2@data$S.delta.OAR, 
                               use = "complete.obs"), 3)
delta.cor.hex.oar

LR.cor.hex.oar <- round(cor(HEX.pred2@data$LR, 
                            HEX.pred2@data$LR.OAR, 
                            use = "complete.obs"), 3)
LR.cor.hex.oar
```

## Plot predicted vs observed in hexagons (OAR method)

```{r, warning=FALSE, message=FALSE, fig.width=10, fig.height=5}
OAR.obspred.HEX.S <- ggplot(data = HEX.pred2@data, 
                      aes(x = S.delta, y = S.delta.OAR)) +
  geom_point(colour = "#377eb8", shape = 1) + 
  geom_point(aes(x = S.gain, y = est.Gain), colour = "#4daf4a", shape = 1) +
  geom_point(aes(x = S.loss, y = est.Loss), colour = "#e41a1c", shape = 1) +
  geom_abline(intercept=0, slope=1) + 
  theme(aspect.ratio=1) + 
  coord_fixed() +
  geom_hline(yintercept=0, linetype =2) +
  geom_vline(xintercept=0, linetype =2) +
  xlim(-60,16) + ylim(-60,16) +
  labs(subtitle = paste("Pearson cor. = ", delta.cor.hex.oar)) +
  xlab("True") + ylab("Predicted") + theme_bw() 

OAR.obspred.HEX.LR <- ggplot(data = HEX.pred2@data, 
                      aes(x = LR, y = LR.OAR)) +
  geom_point(colour = "#377eb8", shape = 1) + 
  geom_abline(intercept=0, slope=1) + 
  theme(aspect.ratio=1) + coord_fixed() +
  geom_hline(yintercept=0, linetype =2) +
  geom_vline(xintercept=0, linetype =2) +
  labs(subtitle = paste("Pearson cor. = ", LR.cor.hex.oar)) +
  xlab("True") + ylab("Predicted") + theme_bw()

grid.arrange(OAR.obspred.HEX.S, OAR.obspred.HEX.LR, nrow=1, ncol=2)
```

# Mapping predictions 

## Predictions in countries

```{r, warning=FALSE, message=FALSE}
CNTR.pred2.fort <-  fortify(CNTR.pred2, region = "LEVEL3_NAM") %>%
              left_join(y = CNTR.pred2@data, by = c("id" = "LEVEL3_NAM"))

pCNTR.SAR <- ggplot(CNTR.pred2.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.delta.SAR)) + blank.theme +
             geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                          fill = NA, colour = "black") +
             coord_fixed() +
             scale_fill_viridis(option = "magma", limits = lims.delta) 

pCNTR.OAR <- ggplot(CNTR.pred2.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.delta.OAR)) + blank.theme +
             geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                          fill = NA, colour = "black") +
             coord_fixed() + 
             scale_fill_viridis(option = "magma",  limits = lims.delta) 
```

## Predictions in hexagons

```{r}
HEX.pred2.fort <-  fortify(HEX.pred2, region = "id") %>%
              left_join(y = HEX.pred2@data, by = "id")

pHEX.SAR <- ggplot(HEX.pred2.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.delta.SAR)) + blank.theme +
             geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                          fill = NA, colour = "black") +
             coord_fixed() +
             scale_fill_viridis(option = "magma", limits = lims.delta) 
pHEX.OAR <- ggplot(HEX.pred2.fort, aes(long, lat, group = group)) + 
             geom_polygon(aes(fill = S.delta.OAR)) + blank.theme +
             geom_polygon(data = LAND.fort,  aes(long, lat, group = group), 
                          fill = NA, colour = "black") +
             coord_fixed() + 
             scale_fill_viridis(option = "magma", limits = lims.delta) 
```

## Plotting prediction maps

```{r, fig.width = 10, fig.height = 12}
lay.mat <- matrix(c(NA, 1, 1,NA,
                    8, 8, 9, 9,
                    2 , 2, 3, 3,
                    4,  4, 5, 5,
                    6, 6, 7, 7), nrow = 5, ncol = 4, byrow=TRUE)
wd <- c(1,1,1,1)
hg <- c(1,0.2,1,1, 1)

grid.arrange(pCNTR.smp + labs(title="(a)", fill = "Available at:", 
                              subtitle="Incomplete data used for all predictions"),
             pCNTR.SAR + labs(title="(b)", subtitle="Predictions, SAR method"),
             pHEX.SAR + labs(title="(c)", subtitle="Predictions, SAR method"),
             pCNTR.OAR + labs(title="(d)", subtitle="Predictions, OAR method"),
             pHEX.OAR + labs(title="(e)",  subtitle="Predictions, OAR method"),
             pCNTR.de + labs(title="(f)",  subtitle="Observed") + 
                        theme(legend.title = element_blank()),
             pHEX.de + labs(title="(g)",   subtitle="Observed")+ 
                        theme(legend.title = element_blank()),
             text_grob("S change in countries", face = "bold"),
             text_grob("S change in hexagons", face = "bold"),
             layout_matrix = lay.mat,
             widths = wd,
             heights = hg)
```

# Final plots

## Observed vs predicted for the main text

```{r, fig.width = 8, fig.height = 4}
obspred.bestof <- grid.arrange(#SAR.obspred.CNTR.S + 
                               #labs(title="(a) Countries, SAR method"), 
                               #OAR.obspred.CNTR.S + 
                               #labs(title="(b) Countries, OAR method"),
                               SAR.obspred.HEX.S + 
                               labs(title="(a) SAR method"), 
                               OAR.obspred.HEX.S + 
                               labs(title="(b) OAR method"), 
                               nrow=1, ncol=2)
```

Export as a png:

```{r}
ggsave("mammals_predicted_vs_true.pdf", obspred.bestof, height = 4, width = 8)
```


## Maps for the main text

```{r, warning=FALSE, message=FALSE}
maps.bestof <- grid.arrange(pCNTR.smp + labs(title="(a)", fill = "Available at:", 
                              subtitle="Incomplete data used for all predictions"),
             
             pHEX.de + labs(title="(b)",   
                            subtitle=TeX(r'($\True \; \hat{S}_{\Delta}$)')) + 
             theme(legend.title = element_blank()),
             
             pHEX.SAR + labs(title="(c)", 
             subtitle=TeX(r'($\Predicted \; \hat{S}_{\Delta} \; from  \; SAR  \; method$)'))+ 
                        theme(legend.title = element_blank()),
             
             pHEX.OAR + labs(title="(d)",  
             subtitle=TeX(r'($\Predicted \; \hat{S}_{\Delta}  \; from \; OAR  \; method$)'))+ 
                        theme(legend.title = element_blank()),
             nrow = 2, ncol = 2)
```

Export as a png:

```{r}
ggsave("mammals_prediction_maps.pdf", maps.bestof, height = 6, width = 10)
```



